---
title: "Module 15 Challenge"
output: html_notebook
---
```{r}
library(readr)
library(tidyverse)
library(dplyr)

#MechaCar_mpg <- read_csv("Desktop/DA2/Module_15_R/Challenge/MechaCar_mpg.csv")
#View(MechaCar_mpg)
```
Deliverable 1
Import the MechaCar_mpg.csv file
```{r}
directory<-"/Users/khadijahm.jack/Desktop/DA2/Module_15_R/Challenge"
Car1<-file.path(directory,"MechaCar_mpg.csv")
MechaCar_mpg1<-read.csv(file = Car1, header=T)

```
Deliverable 2
Import the Suspension_coil.csv file
```{r}
directory1<-"/Users/khadijahm.jack/Desktop/DA2/Module_15_R/Challenge"
Coil1<-file.path(directory1,"MechaCar_mpg.csv")
Suspension_Coil1<-read.csv(file = Coil1, header=T)
```
Deliverable 1
Perform Linear Regression
```{r}
lm(mpg ~vehicle_length + vehicle_weight + spoiler_angle,ground_clearance + AWD, data=MechaCar_mpg1)
```
Deliverable 1: Summary function
```{r}
summary(lm(mpg ~vehicle_length + vehicle_weight + spoiler_angle,ground_clearance + AWD, data=MechaCar_mpg1))
```
Deliverable 2: Create Visualization  
Create a Total Summary Data frame
```{r}
total_summary <- Suspension_Coil %>%  summarize(Mean=mean(PSI),
                                                Median=median(PSI),
                                                Variance=var(PSI),
                                                SD=sd(PSI),.groups='keep')
total_summary

```
Deliverable 2: Lot Summary Data Frame
```{r}
lot_summary <- Suspension_Coil %>% group_by(Manufacturing_Lot) %>% summarize(Mean=mean(PSI),
                                                                                Median=median(PSI),
                                                                                Variance=var(PSI),
                                                                            SD=sd(PSI),.groups='keep')
lot_summary
```
Deliverable 3: T-Test Suspension Coils
```{r}
t.test(Suspension_Coil$PSI, mu=1500)
```
Deliverable 3: T-Test Suspension Coils
Lot1: Subset
```{r}
lot1 <- subset(Suspension_Coil,Manufacturing_Lot =="Lot1")
lot1
```
Lot2: Subset
```{r}
lot2<- subset(Suspension_Coil,Manufacturing_Lot =="Lot2")
lot2
```
Lot3: Subset
```{r}
lot3<- subset(Suspension_Coil,Manufacturing_Lot =="Lot3")
lot3
```
T.Test for Lot1, Lot2, Lot3
```{r}
t.test(lot1$PSI, mu=1500)
t.test(lot2$PSI, mu=1500)
t.test(lot3$PSI, mu=1500)
```
